### 2020-09-02 README.Rmd
Modified those files that needed changes because makehtml had changed how it dealt with addtable and addplot. Hence bare-bones.r and README.Rmd have changed. No Errors, No Warnings, but notes about finding directories in teh check directory (which gets deleted), and the future time stamp issue.

```{r example}
# a minimal example
starttime <- as.character(Sys.time())
library(aMSE)
library(makehtml)
# Obviously you should modify the resdir to suit your own computer
resdir <- "./../../rcode2/aMSEUse/out/testrun"
dirExists(resdir,make=TRUE,verbose=TRUE)
# You now need to ensure that there is a control.csv, reg1sau2pop6.csv
# and zone1.csv file in the data directory
ctrlfiletemplate(resdir)  # puts a template ctrlfile into resdir
zonefiletemplate(resdir)  # puts a template zone file into resdir
datafiletemplate(6,resdir,filename="zone1sau2pop6.csv") # etc
ctrl <- checkresdir(resdir) # checks the data files are present
runname <- ctrl$runlabel    # and reads the control file, if present
zone1 <- readzonefile(resdir,ctrl$zonefile)
glb <- zone1$globals
constants <- readdatafile(glb$numpop,resdir,ctrl$datafile)

out <- setupzone(constants, zone1) # make operating model 
zoneC <- out$zoneC     # constant bits
zoneD <- out$zoneD     # dynamics bits
product <- out$product     # all usually saved in resdir, not here
glb <- out$glb             # now contains the larval movement matrix
  # Are we at equilibrium?
regDe <- testequil(zoneC,zoneD,glb)

@@

reportlist <- list(runname=runname,
                   starttime=starttime,endtime=endtime,
                   zoneC=zoneC, zoneD=zoneD, product=product,
                   glb=glb,constants=constants
)

runnotes <- "This is a bare-bones example."
# If you unhash the make_html component it will generate a local 
# website inside resdir and open it so you can see the results so far.
#
# make_html(replist=reportlist,resdir=resdir,width=500,
#          openfile=TRUE,runnotes=runnotes,verbose=FALSE)

```

>>>>

```{r example}
# a minimal example
starttime <- as.character(Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
# Obviously you should modify the resdir to suit your own computer
resdir <- "./../../A_code/aMSEUse/out/testrun"
dirExists(resdir,make=TRUE,verbose=TRUE)
# The following function calls will ensure that there is a control.csv,
# a zone1sm\au2pop6.csv
# and region1.csv file in the data directory
ctrlfiletemplate(resdir)
zonefiletemplate(resdir)
datafiletemplate(6,resdir,filename="zone1sau2pop6.csv")

ctrl <- checkresdir(resdir)
runname <- ctrl$runlabel
zone1 <- readzonefile(resdir,ctrl$zonefile)
glb <- zone1$globals     # glb without the movement matrix
constants <- readdatafile(glb$numpop,resdir,ctrl$datafile)

out <- setupzone(constants,zone1) # make operating model
zoneC <- out$zoneC
zoneD <- out$zoneD
glb <- out$glb        # glb now has the movement matrix
product <- out$product     # important bits usually saved in resdir
          # did the larval dispersal level disturb the equilibrium?
regDe <- testequil(zoneC,zoneD,glb)

@@

reportlist <- list(runname=runname,
                   starttime=starttime,endtime=endtime,
                   zoneC=zoneC, zoneD=zoneD, product=product,
                   glb=glb,constants=constants)

runnotes <- "This is a bare-bones example."
# If you unhash the make_html call it will generate a local website 
# inside resdir and open it so you can see the results so far.
# make_html(replist=reportlist,resdir=resdir,width=500,
#          openfile=TRUE,runnotes=runnotes,verbose=FALSE,
#          packagename="aMSE",analysis="aMSE")
```
